---
title: "ASDA2 Term Paper"
author: "Matthew Sullivan"
date: "4/25/2022"
output: pdf_document
---

Load dataset.
```{r}
df <- read.csv("/Users/matthewsullivan/Desktop/nba-players.csv",header=TRUE)
head(df)
names(df)
```
X = index
name = name of NBA rookie
gp = games played
min = minutes played
pts = points per game
fgm = field goals made
fga = field goal attempts
fg = field goal percentage
X3p_made = 3 points made
X3pa = 3 point attempts
X3p = 3 point percentage
ftm = free throw made
fta = free throw attempts
ft = free throw percentage
oreb = offensive rebounds
dreb = defensive rebounds
reb = rebounds
ast = assists
stl = steals
blk = blocks
tov = turnovers
target_5yrs = Career Duration 5 years or longer?

All figures are per-game averages.
More data can be found at https://www.nba.com/stats/players/traditional/?SeasonType=Regular%20Season&sort=PTS&dir=-1&Season=2021-22&PlayerExperience=Rookie

```{r}
summary(df)
colSums(is.na(df) | df == "") #No NAs in data.
target_perc = sum(df$target_5yrs)/length(df$target_5yrs)
target_perc #62% of rookies have a career that lasts 5 years or longer, nice!
```

```{r}
#plot(df$X,df$gp)
#plot(df$X,df$min)
#plot(df$X,df$pts)
#plot(df$X,df$fg)
#plot(df$X,df$X3p)
#plot(df$X,df$ft)
#plot(df$X,df$oreb)
#plot(df$X,df$dreb)
#plot(df$X,df$ast)
#plot(df$X,df$stl)
#plot(df$X,df$blk)
#plot(df$X,df$tov)
```
No variables show any need to explore potential outliers.

```{r}
#install.packages("corrplot")
library(corrplot)
df_corrplot <- df[, -which(names(df) %in% c("X", "name", "target_5yrs"))]
M = cor(df_corrplot)
corrplot(M,diag = FALSE)
```
We see noteworthy correlation between a few variables --
A) Minutes played has a strong positive relationship with many variables, of which Field Goals and Free Throws stand out. This is different from Games playes, which has a lower positive correlation across variables, indicating that Minutes played has a stronger relationship to higher performance.
B) Similar variables (e.g. Free Throws Made and Free Throw attempts) naturally share strong positive relationships. Note that percentage statistics (e.g. free throw percentage) have little correlation to other variables, whereas their counterpart points made and attempts do.
C) Defensive statistics (e.g. offensive rebounds, blocks) share slight negative relationships with 3-point statistics. Also, 3 point statistics share a slight negative relationship with Field Goals. Perhaps there's a variable missing -- position -- which might help to explain difference in performance among players.

```{r}
plot(df$fgm,df$X3p_made)
plot(df$fgm,df$ftm)
plot(df$ftm,df$X3p_made)
plot(df$fgm,df$oreb)
plot(df$fgm,df$dreb)
```

