---
title: "ASDA2 Model Creation"
output: html_notebook
---

```{r}
df <- read.csv("nba-players.csv", header=TRUE)
```



Making our own dataset from original datasets.

```{r}
rooks <- read.csv("NBA Rookies by Year.csv", header=TRUE)
names(rooks)[1] <- "rPlayer"
player_years <- read.csv("NBA Players by State.csv", header=TRUE)
names(player_years)[1] <- "pPlayer"
player_years <- player_years[, c("pPlayer", "Yrs", "G")]
```

```{r}
library(sqldf)
```

```{r}
as.double.factor <- function(x) {as.numeric(levels(x))[x]}
```

```{r}
new_df = na.omit(sqldf("
  SELECT *
  FROM rooks r
    JOIN player_years p ON r.rPlayer = p.pPlayer
"))
new_df$Yrs <- as.numeric(as.character(new_df$Yrs))
new_df$G <- as.numeric(as.character(new_df$G))
new_df$X3P. <- as.double.factor(new_df$X3P.)
new_df[is.na(new_df)] <- 0
```

```{r}
write.csv(df,"rookies.csv", row.names = FALSE)
```


```{r}
head(new_df)
```

```{r}
hist(new_df$Year.Drafted)
```

```{r}
hist(new_df$Yrs)
```

```{r}
plot(new_df$Year.Drafted, new_df$Yrs)
```

```{r}
summary(new_df$Yrs)
```

What happens if we get rid of the most recent players - they are somewhat skewing the data because a player in 2015, for example, can only have a max Yrs of 2!
We will get omit the rookies from the last 5 yrs now and see what we have.
```{r}
old_players <- new_df[new_df$Year.Drafted < 2001, ]
```

```{r}
summary(old_players$Yrs)
```
Our average Yrs has went up in this new dataset.

```{r}
max(new_df[new_df$Year.Drafted == 2012, ]$Yrs)
```
The highest possible years for someone drafted in 2012 is 5 years (this dataset was made in 2016).
Maybe we should make a cutoff at 5 years and do ordinal.

```{r}
target_yrs <- old_players$Yrs
plot(target_yrs)
```

```{r}
target_yrs[target_yrs > 5] <- 5
plot(target_yrs)
old_players$target_yrs <- target_yrs
```
```{r}
old_players
```


Test train split
```{r}
smp_size <- floor(0.75 * nrow(old_players))

set.seed(614)
train_ind <- sample(seq_len(nrow(old_players)), size = smp_size)

train <- old_players[train_ind, ]
test <- old_players[-train_ind, ]

all_old <- subset(old_players, select = -c(`rPlayer`, `pPlayer`, `target_yrs`, `G`, `Year.Drafted`))
test <- subset(test, select = -c(`rPlayer`, `pPlayer`, `target_yrs`, `G`, `Year.Drafted`))
train <- subset(train, select = -c(`rPlayer`, `pPlayer`, `target_yrs`, `G`, `Year.Drafted`))
```



```{r}
fit <- lm(Yrs ~ . , data=train)
summary(fit)
```

MSE for test data
```{r}
preds <- predict(fit, newdata=test)
mean((test$Yrs - preds)^2)
```

```{r}
plot(test$Yrs, preds)
abline(0,1)
```

```{r}
plot(fitted(fit), resid(fit))
abline(0,0, col="red")
```







